---
title: "Week 3 Assignment - R Character Manipulation and Date Processing"
author: "Kalyanaraman Parthasarathy"
output:
  html_document:
    code_folding: show
    depth: 4
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# RPubs link - http://rpubs.com/kalyanparthasarathy/308799

# Check if the package is installed. If not, install the package
if(!require('stringr')) {
  install.packages('stringr')
  library(stringr)
}

raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))

```

### Problem 3

Copy the introductory example. The vector name stores the extracted names.
R> name
     [1] "Moe Szyslak"       "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
     [4] "Ned Flanders"      "Simpson, Homer"       "Dr. Julius Hibbert"
(a) Use the tools of this chapter to rearrange the vector so that all elements conform to thestandardfirst_name last_name.
(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
(c) Construct a logical vector indicating whether a character has a second name.

```{r}

# (a). Use the tools of this chapter to rearrange the vector so that all elements conform to thestandardfirst_name last_name.
firtName_LastName <- unlist(sub("([A-z]{1,}),  *([A-z]{1,})", "\\2 \\1", sub("[A-z]{1,}\\. "," ",name)))
firtName_LastName

# (b). Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
tileCheckVector <- c(str_detect(name, "(^[A-z]{1,}\\. ).*"))
tileCheckDF <- data.frame(name, tileCheckVector)
names(tileCheckDF) <- c("Name", "Has Title?")
tileCheckDF

# (c). Construct a logical vector indicating whether a character has a second name.
secondNameCheckVector <- str_detect(name, " [A-z]{1,}\\. ")
secondNameCheckDF <- data.frame(name, secondNameCheckVector)
names(secondNameCheckDF) <- c("Name", "Has Second Name?")
secondNameCheckDF

```

### Problem 4

Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.
(a) [0-9]+\\$
(b) \\b[a-z]{1,4}\\b
(c) .*?\\.txt$
(d) \\d{2}/\\d{2}/\\d{4}
(e) <(.+?)>.+?</\\1>

```{r}

# (a) [0-9]+\\$ - N number of digits followed by $
cat("\014")
q4aData <- c("Kalyan: 4073647173$", "Partha: 4073647173")
q4aDataDF <- data.frame(q4aData, str_detect(q4aData, "[0-9]+\\$"))
names(q4aDataDF) <- c("Data", "Pattern Matched?")
q4aDataDF

# (b) \\b[a-z]{1,4}\\b
namesList <- c("tom phan", "chris esser", "eric fisher", "james johnson")
namesListDF <- data.frame(namesList, str_detect(namesList, "\\b[a-z]{1,4}\\b"))
names(namesListDF) <- c("Name", "Pattern Matched?")
namesListDF

# (c) .*?\\.txt$
filesList <- c("ReadMe.txt", "index.html", "setup.ini", "resume.txt")
filesListDF <- data.frame(filesList, str_detect(filesList, ".*?\\.txt$"))
names(filesListDF) <- c("File Name", "Pattern Matched?")
filesListDF

# (d) \\d{2}/\\d{2}/\\d{4}
dobList <- c("03/05/1981", "02-09-1976", "04/05/2005", "05-22-2010")
dobListDF <- data.frame(dobList, str_detect(dobList, "(\\d{2}/\\d{2}/\\d{4})"))
names(dobListDF) <- c("DOB", "Pattern Matched?")
dobListDF

# (e) <(.+?)>.+?</\\1>
htmlScript <- c("<table>Table</table>", "<tr>Rows</tr>", "<td>Improper cell definition<td>")
htmlScriptDF <- data.frame(htmlScript, str_detect(htmlScript, "<(.+?)>.+?</\\1>"))
names(htmlScriptDF) <- c("HTML Syntax", "Pattern Matched?")
htmlScriptDF


```

### Problem 9

The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.
clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}

dataString <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
dataStringDecoded <- unlist(str_extract_all(dataString, "[[:upper:].]{1,}"))
dataStringDecoded <- str_replace_all(paste(dataStringDecoded, collapse = ''), fixed("."), " ")
dataStringDecoded

```
